---
title: "EPI 590R Final Project"
author: "Carson Bohl"
format: html
editor: visual
---
```{r}
#| echo: false 
#| output: false
library(gtsummary)
library(tidyverse)

```

```{r}
#| echo: false 
#| output: false
#Read in dataset
Pride_Index_Data <- read.csv(here::here("Data", "pride_index_data.csv"))
```

```{r}
#| echo: false 
#| output: false
#Create new variable because original dataset has value missing if it's false
Pride_Index_Data$liberal_arts1 <- ifelse(is.na(Pride_Index_Data$liberal_arts), FALSE, TRUE)

Pride_Index_Data$religious1 <- ifelse(is.na(Pride_Index_Data$religious), FALSE, TRUE)

Pride_Index_Data$public1 <- ifelse(is.na(Pride_Index_Data$public), FALSE, TRUE)

Pride_Index_Data$residential1 <- ifelse(is.na(Pride_Index_Data$residential), FALSE, TRUE)

Pride_Index_Data$hbcu1 <- ifelse(is.na(Pride_Index_Data$hbcu), FALSE, TRUE)
```

This data comes from Campus Pride Index and provides a LGBTQ national benchmarking tool for colleges and universities to create safer, more inclusive campus communities. The platform allows prospective students, families/parents and those interested in higher education to search a database of LGBTQ-friendly campuses who have come out to improve the academic experience and quality of campus life. @tbl-one presents descriptive statistics. 
```{r}
#| echo: false
#| label: tbl-one
#| tbl-cap: "Descriptive Statistics"
table1 <- tbl_summary(
	Pride_Index_Data,
	include = c(rating, students,
							community_type,
					residential1, liberal_arts1, religious1,
							hbcu1),
	label = list(
		rating ~ "Climate Rating",
		students ~ "Number of Students",
		community_type ~ "Type of Community",
		residential1 ~ "Residential",
		liberal_arts1 ~ "Liberal Arts",
		religious1 ~ "Religious",
		hbcu1 ~ "HBCU"
	),
	missing_text = "Missing"
)
table1
```


```{r} 
#| echo: false
#| output: false
#Apply function so I can use it for an inline statistic
prop <- function(x, multiplier) {
  n <- length(x)
  mean_val <- multiplier * sum(x) / n
  return(mean_val)
}

prop(Pride_Index_Data$religious1, multiplier=100)
```


```{r}
#| echo: false
#| output: false
inline_text(table1, variable="students", column="stat_0")
stat <- prop(Pride_Index_Data$public1, multiplier=100)
```
The median number of students was (`r inline_text( table1, variable = "students", column="stat_0")`). `r stat`% of the colleges/universities are public. 



@tbl-two presents univariate regression results depicting the relationship between the number of students and two other characteristics: liberal arts curriculum and religious affiliation. 
```{r}
#| echo: false
#| label: tbl-two
#| tbl-cap: "Regression Results"
tbl_uvregression(
	Pride_Index_Data,
	y = students,
	include = c(liberal_arts1, religious1
	),
	method = lm
)
```

```{r}

```

@fig-hist shows the distribution of the number of students across the colleges/universities. 
```{r}
#| echo: false
#| label: fig-hist
#| fig-cap: Histogram Depicting Number of Students 
hist(Pride_Index_Data$students)
```






